\cvsection{Professional Experience}

\role{IT Solutions Architect}{2024 - Present}{NTT DATA, consulting assignment for the European Commission}{Luxembourg}
\begin{itemize}
  \item Design secure infrastructure and Remote Access solutions for European Commission environments used by institutions, agencies, staff and external providers.
  \item Challenged a 259-requirement MoSCoW matrix against Warpgate and completed the product assessment against Compliance requirements and Core Features.
  \item Define technical architectures, standards, automation, validation approach and documentation.
  \item Work with Product Owners, Project Managers, architects, Network Security, Linux, Cloud, CMDB, Compliance and SOC teams.
  \item Support projects related to Remote Access modernization, AWS administrative access and automated platform delivery.
\end{itemize}

\role{Remote Access Technical Lead}{2021 - 2024}{NTT Ltd. / NTT DATA, consulting assignment for the European Commission}{Luxembourg}
\begin{itemize}
  \item Main technical reference for Remote Access platforms in a critical 24/7 production context serving around 40,000 users.
  \item Worked on expert support, architecture input, platform evolution, impact analysis and support for Network Security teams.
  \item Contributed to the move from proprietary VPN technologies to Open Source and more automated platforms.
\end{itemize}

\role{Network Security Engineer}{2015 - 2021}{Dimension Data / NTT Ltd., consulting assignment for the European Commission}{Luxembourg}
\begin{itemize}
  \item Operated and evolved security services including firewalling, reverse proxy, proxy, DNS, load balancing, WAF and remote access.
  \item Supported major Remote Access capacity changes, including COVID scaling with F5 load balancing and VMware appliances.
  \item Built a broad understanding of production infrastructure, security constraints and change management.
  \item Progressively specialized in Remote Access and became an escalation point for VPN platform operations and evolution.
\end{itemize}
